---
title: "Chapter05"
author: "Xiaoyan Yue"
date: "5/9/2017"
output: 
  html_document: 
    keep_md: yes
    number_sections: yes
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(nycflights13)
library(tidyverse)

flights

filter(flights, month == 1, day == 1)
jan1 <- filter(flights, month == 1, day == 1)

(dec25 <- filter(flights, month == 12, day == 25))

filter(flights, month == 1)

filter(flights, month == 11 | month == 12)

filter(flights, month %in% c(11, 12))

filter(flights, !(arr_delay > 120 | dep_delay > 120))
filter(flights, arr_delay <= 120, dep_delay <= 120)

df <- tibble(x = c(1, NA, 3))
filter(df, x > 1)

filter(df, is.na(x) | x > 1)

flights_sml <- select(flights, 
  year:day, 
  ends_with("delay"), 
  distance, 
  air_time
)
mutate(flights_sml,
  gain = arr_delay - dep_delay,
  speed = distance / air_time * 60
)

mutate(flights_sml,
  gain = arr_delay - dep_delay,
  hours = air_time / 60,
  gain_per_hour = gain / hours
)

transmute(flights,
  gain = arr_delay - dep_delay,
  hours = air_time / 60,
  gain_per_hour = gain / hours
)

(x <- 1:10)
lag(x)
lead(x)
```
 
#Exercise 5.2.3 
##1.Find all flights that 
###(1)Had an arrival delay of two or more hours
```{r}
filter(flights, arr_delay > 120)
```

###(2)Flew to Houston (IAH or HOU)
```{r}
filter(flights, dest == "IAH"|dest=="HOU")
```

###(3)Were operated by United, American, or Delta
```{r}
filter(flights, carrier == "UA"|carrier =="DL")
```

###(4)Departed in summer (July, August, and September) 
```{r}
?flight
```

###(5)Arrived more than two hours late, but didn’t leave late
```{r}
filter(flights, arr_delay >= 120|dep_delay <=0)
```

###(6)Were delayed by at least an hour, but made up over 30 minutes in flight
```{r}
filter(flights, dep_delay >= 60, arr_delay <= 30)
```

###(7)Departed between midnight and 6am (inclusive)  
```{r}
filter(flights, dep_time >= 42 , dep_time <= 600)
```

 
##2.Another useful dplyr filtering helper is between(). What does it do? Can you use it to simplify the code needed to answer the previous challenges?
```{r}
filter(flights, between(dep_time,42,600))

```


##3.How many flights have a missing dep_time? What other variables are missing? What might these rows represent?
```{r}
filter(flights, is.na(flights$dep_time))
#the dep_delay,arr_time,arr_delay are missing, they might represent cancelled flights.
```

##4.Why is NA ^ 0 not missing? Why is NA | TRUE not missing? Why is FALSE & NA not missing? Can you figure out the general rule? (NA * 0 is a tricky counterexample!)
```{r}
#since NA^0 is 0, NA|TRUE is NA and TRUE,it's TRUE; FALSE & NA is FALSE or NA, it's TRUE
```

#5.3.1 Exercises

##1. How could you use arrange() to sort all missing values to the start? (Hint: use is.na()).
```{r}
arrange(flights, desc(is.na(dep_time)))

```

##2. Sort flights to find the most delayed flights. Find the flights that left earliest.
```{r}
arrange(flights, desc(dep_delay))

arrange(flights, desc(dep_time))

```


##3. Sort flights to find the fastest flights.
```{r}
arrange(flights, desc(air_time/distance))

```


##4. Which flights travelled the longest? Which travelled the shortest? 
```{r}
arrange(flights, desc(distance))

```

#5.4.1 Exercises

##1. Brainstorm as many ways as possible to select dep_time, dep_delay, arr_time, and arr_delay from flights.
```{r}
select(flights,dep_time,dep_delay,arr_time,arr_delay)
select(flights,starts_with("dep"),starts_with("arr"))
select(flights,c(4,6,7,9))
```

##2. What happens if you include the name of a variable multiple times in a select() call?
```{r}
select(flights,dep_time,dep_time,dep_time)
```

##3. What does the one_of() function do? Why might it be helpful in conjunction with this vector?
```{r}
vars <- c("year", "month", "day", "dep_delay", "arr_delay")
select(flights,one_of(vars))
```

##4. Does the result of running the following code surprise you? How do the select helpers deal with case by default? How can you change that default?

```{r}
select(flights, contains("TIME"))
select(flights, contains("TIME",ignore.case = FALSE))#Change 'ignore.case = TRUE'to ignore.case = FALSE

```
 
#5.5.2 Exercises

##1. Currently dep_time and sched_dep_time are convenient to look at, but hard to compute with because they’re not really continuous numbers. Convert them to a more convenient representation of number of minutes since midnight.
```{r}
flights

transmute(flights,
          dep_time, sched_dep_time,
          dep_hour = dep_time %/% 100,
          dep_minute = dep_time %% 100,
          dep_time_minutes=dep_hour*60 + dep_minute,
          sched_dep_hour=sched_dep_time%/% 100,
          sched_dep_minute = sched_dep_time%% 100,
          sched_dep_time_minutes = sched_dep_hour*60 + sched_dep_minute)
```


##2. Compare air_time with arr_time - dep_time. What do you expect to see? What do you see? What do you need to do to fix it?
```{r}
transmute(flights,
          air_time,
          air_time2=arr_time - dep_time)

#how to fix it???
```


##3. Compare dep_time, sched_dep_time, and dep_delay. How would you expect those three numbers to be related?
```{r}
select(flights,dep_time, sched_dep_time, dep_delay)
#I expected that dep_delay equals to dep_time milus sched_dep_time
```
##4. Find the 10 most delayed flights using a ranking function. How do you want to handle ties? Carefully read the documentation for min_rank().
```{r}
flights

flights %>% filter(!(is.na(dep_time)),!(is.na(arr_time))) %>% filter(rank(desc(arr_delay))<=10)

flights %>% filter(min_rank(desc(arr_delay))<=10)
```

##5. What does 1:3 + 1:10 return? Why?
```{r}
1:3 + 1:10
x <- c(1,2,3)
y <- c(1,2,3,4,5,6,7,8,9,10)
z <- c(1+1,2+2,3+3,1+4,2+5,3+6,1+7,2+8,3+9,1+10)

z==x+y
##If the longer object is a multiple of the shorter, this amounts to simply repeating the shorter object several times. Oftentimes R programmers will take advantage of this to do things more compactly and with less typing.
```
##6. What trigonometric functions does R provide?

