---
title: "Chapter07-1"
author: "Xiaoyan Yue"
date: "5/23/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(gridExtra)
```

#7.3.4 Exercises

##1.Explore the distribution of each of the x, y, and z variables in diamonds. What do you learn? Think about a diamond and how you might decide which dimension is the length, width, and depth.
```{r}
diamonds %>% select(x,y,z)
#x
x <- ggplot(data = diamonds, mapping = aes(x = x)) +
  geom_histogram(binwidth = 0.01) +
  coord_cartesian(xlim = c(3, 12))
#y
y <- ggplot(data = diamonds, mapping = aes(x = y)) +
  geom_histogram(binwidth = 0.01) +
  coord_cartesian(xlim = c(3, 12))
#z
z <- ggplot(data = diamonds, mapping = aes(x = z)) +
  geom_histogram(binwidth = 0.01) +
  coord_cartesian(xlim = c(0, 8))

grid.arrange(x,y,z,ncol=3,nrow=1)

help("diamonds")#it will tell us, x is length in mm, y is width in mm, z is depth in mm.
#x and y have similar distribution. I think x and y are length and width respectively, but z is depth.
```

##2.Explore the distribution of price. Do you discover anything unusual or surprising? (Hint: Carefully think about the binwidth and make sure you try a wide range of values.)
```{r}
price <- diamonds %>% select(price)

p1 <- ggplot(data = price, mapping = aes(x = price)) +
  geom_histogram(binwidth = 100)

p1_zoom <- ggplot(data = price, mapping = aes(x = price)) +
  geom_histogram(binwidth = 10) +
  coord_cartesian(xlim = c(0, 2500))

grid.arrange(p1,p1_zoom,ncol=1,nrow=2)
```


##3.How many diamonds are 0.99 carat? How many are 1 carat? What do you think is the cause of the difference?
```{r}
diamonds %>% filter(carat>=0.99,carat<=1) %>% count(carat)

ggplot(data = diamonds, mapping = aes(x = carat)) +
  geom_histogram(binwidth = 0.01) +
  coord_cartesian(xlim = c(0.99, 1))
  
```


##4.Compare and contrast coord_cartesian() vs xlim() or ylim() when zooming in on a histogram. What happens if you leave binwidth unset? What happens if you try and zoom so only half a bar shows?
```{r}
original <- ggplot(diamonds) + 
  geom_histogram(mapping = aes(x = y), binwidth = 0.5) +
  coord_cartesian(ylim = c(0, 50))

original_xlim <- ggplot(diamonds) + 
  geom_histogram(mapping = aes(x = y), binwidth = 0.5) +
  coord_cartesian(xlim = c(0, 20))

original_binwidth <- ggplot(diamonds) + 
  geom_histogram(mapping = aes(x = y)) +
  coord_cartesian(ylim = c(0, 50))

original_xlim_binwidth <- ggplot(diamonds) + 
  geom_histogram(mapping = aes(x = y)) +
  coord_cartesian(xlim = c(0, 20))

grid.arrange(original,original_xlim,original_binwidth,original_xlim_binwidth,ncol=1,nrow=4)
```
#7.4.1 Exercises 
##1.What happens to missing values in a histogram? What happens to missing values in a bar chart? Why is there a difference?
```{r}
?geom_histogram
?geom_bar

#NA could be a catagorical variable in the plot

#the stat of them are different, the stat in geom_bar is "count",while that in geom_histogram is "bin"

```

##2.What does na.rm = TRUE do in mean() and sum()?
```{r}
#remove NAs when calculating mean and sum of the data
```

