---
title: "Chapter05-2"
author: "Xiaoyan Yue"
date: "5/15/2017"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(nycflights13)
library(tidyverse)
```
#5.6.7 Exercise
##1. Brainstorm at least 5 different ways to assess the typical delay characteristics of a group of flights. Consider the following scenarios:
```{r}
#show data
flights
```


### A flight is 15 minutes early 50% of the time, and 15 minutes late 50% of the time.
```{r}

```


### A flight is always 10 minutes late.
```{r}

```

### A flight is 30 minutes early 50% of the time, and 30 minutes late 50% of the time.
```{r}

```

### 99% of the time a flight is on time. 1% of the time it’s 2 hours late.

### Which is more important: arrival delay or departure delay?

##2. Come up with another approach that will give you the same output as not_cancelled %>% count(dest) and not_cancelled %>% count(tailnum, wt = distance) (without using count()).
```{r}
not_cancelled %>% dplyr::count(dest)#count the total number of flight in each group
not_cancelled %>% dplyr::count(tailnum, wt = distance)# “count” (sum) the total number of miles a plane flew with a weight variable

not_cancelled %>% group_by(dest) %>% dplyr::summarise(n=n())
not_cancelled %>% group_by(tailnum) %>% dplyr::summarise(flights=sum(distance))

?n
```

##3. Our definition of cancelled flights (is.na(dep_delay) | is.na(arr_delay) ) is slightly suboptimal. Why? Which is the most important column?
```{r}
not_cancelled <- flights %>% 
  filter(!is.na(dep_delay), !is.na(arr_delay))

not_cancelled <- flights %>% 
  filter(!is.na(dep_time), !is.na(arr_time))#dep_time and arr_time are the most important columns
```

##4. Look at the number of cancelled flights per day. Is there a pattern? Is the proportion of cancelled flights related to the average delay?
```{r}
cancelled_flights <- flights %>% filter(is.na(dep_time), is.na(arr_time)) %>% group_by(year,month,day) %>% dplyr::summarise(n=n())
ggplot() + 
  geom_freqpoly(data = cancelled_flights, mapping = aes(x = n),binwidth = 10)

delays <- not_cancelled %>% 
  group_by(tailnum) %>% 
  dplyr::summarise(
    delay = mean(arr_delay, na.rm = TRUE),
    n = n()
  )

ggplot() + 
  geom_point(data = delays, mapping = aes(x = n, y = delay),alpha = 1/10) + 
  geom_freqpoly(data = cancelled_flights, mapping = aes(x = n),binwidth = 10)
```


##5. Which carrier has the worst delays? Challenge: can you disentangle the effects of bad airports vs. bad carriers? Why/why not? (Hint: think about flights %>% group_by(carrier, dest) %>% summarise(n()))
```{r}
delay_carrier_dest <- flights %>% group_by(carrier, dest) %>% dplyr::summarise(n=n(),delay=mean(arr_delay,na.rm=TRUE))
ggplot(data = delay_carrier_dest, mapping = aes(x = dest, y = delay, color=carrier)) +
  geom_point(aes(size=n),alpha = 1/2) +
  #geom_smooth(mapping=aes(group=carrier),se=FALSE) + 
  theme(axis.title.x=element_blank(),axis.text.x = element_text(angle = 90, hjust = 1, size = 8))
#I think, for carrier, EV has the worst delays; OO has the worst delays at DSM and OMA; UA has the worst delay at SRO 

```

##6. What does the sort argument to count() do. When might you use it?
```{r}
?count
#sort if TRUE will sort output in descending order of n

#for example, if I want to know which carrier has the largest number of flights
flights %>% 
  dplyr::count(carrier, sort=TRUE)
```

#5.7.1 Exercise
##1. Refer back to the lists of useful mutate and filtering functions. Describe how each operation changes when you combine it with grouping.
```{r}
#it could be equally applied to every group
```

##2. Which plane (tailnum) has the worst on-time record?
```{r}
not_cancelled %>% group_by(tailnum) %>% dplyr::count(tailnum,sort = TRUE)

not_cancelled %>% group_by(tailnum) %>% dplyr::mutate(ave_delay=mean(arr_delay)) %>% arrange(desc(ave_delay)) %>% select(year:day,tailnum,ave_delay)
```

##3. What time of day should you fly if you want to avoid delays as much as possible?
```{r}
dep_choose <- not_cancelled %>% mutate(dep_hour=sched_dep_time%/%100) %>% group_by(dep_hour) %>% filter(arr_delay>0) %>% dplyr::summarise(n=n(),ave_delay=mean(arr_delay)) %>% arrange(ave_delay)

ggplot(data = dep_choose,mapping=aes(x=dep_hour,y=ave_delay))+
  geom_col()+
  geom_smooth()
```

##4. For each destination, compute the total minutes of delay. For each, flight, compute the proportion of the total delay for its destination.
```{r}
not_cancelled %>% group_by(dest) %>% dplyr::summarise(tot_delay=sum(arr_delay,na.rm = T)) %>% arrange(desc(tot_delay))#if there is any NA in the form, the calculation will return a NA for that group


not_cancelled %>% group_by(flight) %>% dplyr::mutate(total_delay = sum(arr_delay,na.rm = T)) %>% group_by(flight,dest) %>% dplyr::summarise (prop_delay=sum(arr_delay,na.rm = T)/total_delay)
```

##5. Delays are typically temporally correlated: even once the problem that caused the initial delay has been resolved, later flights are delayed to allow earlier flights to leave. Using lag() explore how the delay of a flight is related to the delay of the immediately preceding flight.
```{r}

```

##6. Look at each destination. Can you find flights that are suspiciously fast? (i.e. flights that represent a potential data entry error). Compute the air time a flight relative to the shortest flight to that destination. Which flights were most delayed in the air?
```{r}
not_cancelled %>% group_by(origin,dest) %>% dplyr::mutate(n=n(),ave_air_time=sum(air_time)/n)
```

##7. Find all destinations that are flown by at least two carriers. Use that information to rank the carriers.
```{r}
flights %>% group_by(dest) %>% dplyr::count(carrier)

flights %>% count(dest, wt = carrier)
```

##8. For each plane, count the number of flights before the first delay of greater than 1 hour.
```{r}

```

#Run the code in the book
##summarise
```{r}
summarise(flights, delay = mean(dep_delay, na.rm = TRUE))
```

##group_by, summarise
```{r}
by_day <- group_by(flights, year, month, day)
summarise(by_day, delay = mean(dep_delay, na.rm = TRUE))
```

##group_by,summarise
```{r}
by_dest <- group_by(flights, dest)
delay <- summarise(by_dest,
  count = n(),
  dist = mean(distance, na.rm = TRUE),
  delay = mean(arr_delay, na.rm = TRUE)
)
delay <- filter(delay, count > 20, dest != "HNL")

ggplot(data = delay, mapping = aes(x = dist, y = delay)) +
  geom_point(aes(size = count), alpha = 1/3) +
  geom_smooth(se = FALSE)
```
##group_by, summarise, filter,%>%
```{r}
delays <- flights %>% 
  group_by(dest) %>% 
  summarise(
    count = n(),
    dist = mean(distance, na.rm = TRUE),
    delay = mean(arr_delay, na.rm = TRUE)
  ) %>% 
  filter(count > 20, dest != "HNL")
```
##na.rm
```{r}
flights %>% 
  group_by(year, month, day) %>% 
  summarise(mean = mean(dep_delay))

flights %>% 
  group_by(year, month, day) %>% 
  summarise(mean = mean(dep_delay, na.rm = TRUE))
```

##
```{r}
not_cancelled <- flights %>% 
  filter(!is.na(dep_delay), !is.na(arr_delay))

not_cancelled %>% 
  group_by(year, month, day) %>% 
  summarise(mean = mean(dep_delay))
```

##counts
```{r}
delays <- not_cancelled %>% 
  group_by(tailnum) %>% 
  dplyr::summarise(
    delay = mean(arr_delay)
  )

ggplot(data = delays, mapping = aes(x = delay)) + 
  geom_freqpoly(binwidth = 10)
```
##scatterplot
```{r}
delays <- not_cancelled %>% 
  group_by(tailnum) %>% 
  dplyr::summarise(#to avoid confusions with masking functions, it is clear to use the "package::function" specification
    delay = mean(arr_delay, na.rm = TRUE),
    n = n()
  )

ggplot(data = delays, mapping = aes(x = n, y = delay)) + 
  geom_point(alpha = 1/10)
```
##
```{r}
delays %>% 
  filter(n > 25) %>% 
  ggplot(mapping = aes(x = n, y = delay)) + 
    geom_point(alpha = 1/10)


```
##Plot the skill of the batter (measured by the batting average, ba) against the number of opportunities to hit the ball (measured by at bat, ab)
###load the data
```{r}
library(Lahman)
# Convert to a tibble so it prints nicely
batting <- as_tibble(Lahman::Batting)
```
###plot
```{r}
batters <- batting %>% 
  group_by(playerID) %>% 
  dplyr::summarise(
    ba = sum(H, na.rm = TRUE) / sum(AB, na.rm = TRUE),
    ab = sum(AB, na.rm = TRUE)
  )

batters %>% 
  filter(ab > 100) %>% 
  ggplot(mapping = aes(x = ab, y = ba)) +
    geom_point() + 
    geom_smooth(se = FALSE)
#> `geom_smooth()` using method = 'gam'
```
 
##ranking
```{r}
batters %>% 
  arrange(desc(ba))
```
```{r}
not_cancelled %>% 
  group_by(year, month, day) %>% 
  dplyr::summarise(
    avg_delay1 = mean(arr_delay),
    avg_delay2 = mean(arr_delay[arr_delay > 0]) # the average positive delay
  )
```

##Measures of spread
```{r}
# Why is distance to some destinations more variable than to others?
not_cancelled %>% 
  group_by(dest) %>% 
  dplyr::summarise(distance_sd = sd(distance)) %>% 
  arrange(desc(distance_sd))
```

##Measures of rank
```{r}
not_cancelled %>% 
  group_by(year,month,day) %>% 
  dplyr::summarise(
    first=min(dep_time),
    last =max(dep_time)
  )
```

##Measure of position
```{r}
not_cancelled %>% 
  group_by(year,month,day) %>% 
  dplyr::summarise(
    first_dep = first(dep_time),
    Seventh_dep = nth(dep_time,7),
    last_dep = last(dep_time)
  )
```

##Filtering on ranks
```{r}
not_cancelled %>% 
  group_by(year, month, day) 
```
```{r}
not_cancelled %>% 
  group_by(year, month, day) %>% 
  mutate(r = min_rank(desc(dep_time))) %>% 
  filter(r %in% range(r))

```
# Which destinations have the most carriers? n_distinct, count the number of unique items
```{r}
not_cancelled %>% 
  group_by(dest) %>% 
  dplyr::summarise(carriers = n_distinct(carrier)) %>% 
  arrange(desc(carriers))
```
##count
```{r}
not_cancelled %>% 
  dplyr::count(dest)
```
##optionally provide a weight variable for count
```{r}
not_cancelled %>% 
  dplyr::count(tailnum, wt = distance)
```
##Counts and proportions of logical values, sum(x) gives the number of TRUEs in x, and mean(x) gives the proportion
### How many flights left before 5am? (these usually indicate delayed flights from the previous day)
```{r}
not_cancelled %>% 
  group_by(year, month, day) %>% 
  dplyr::summarise(n_early = sum(dep_time < 500))
```
### What proportion of flights are delayed by more than an hour?
```{r}
not_cancelled %>% 
  group_by(year, month, day) %>% 
  dplyr::summarise(hour_perc = mean(arr_delay > 60))
```

##Grouping by mutiple variables
```{r}
daily <- group_by(flights, year, month, day)
(per_day   <- dplyr::summarise(daily, flights = n()))

(per_month <- dplyr::summarise(per_day, flights = sum(flights)))
(per_year  <- dplyr::summarise(per_month, flights = sum(flights)))
```
##ungrouping
```{r}
daily %>% 
  ungroup() %>%             # no longer grouped by date
  dplyr::summarise(flights = n())  # all flights
```
##find the worst 9 members of each group
```{r}
flights_sml %>% 
  group_by(year, month, day) %>%
  filter(rank(desc(arr_delay)) < 10)#filtered the flight which was ranked lower than 10 in each of the group
```

##Find groups bigger than a threshold
```{r}
popular_dests <- flights %>% 
  group_by(dest) %>% 
  filter(n() > 365)#filtered groups have more than 365 destinations
popular_dests
```

##Standardise to compute per group metrics:
```{r}
popular_dests %>% 
  filter(arr_delay > 0) %>% 
  mutate(prop_delay = arr_delay / sum(arr_delay)) %>% #calculate probability of arr_delay for each group
  select(year:day, dest, arr_delay, prop_delay)#select those columns for all groups
```

