---
title: "RClub_Assignment03"
author: "Xiaoyan Yue"
date: "4/24/2017"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache= TRUE, autodep = TRUE)
```

#Load the packages
```{r}
library(tidyverse)
library(ggplot2)
theme_set(theme_grey(12))
```

  
#Practise on mpg
```{r}
mpg
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))
```

  
#Practise 3.2.4
  
##Run ggplot(data = mpg) what do you see?
```{r}
ggplot(data = mpg)#nothing
```
  
##How many rows are in mtcars? How many columns?
```{r}
dim(mtcars)
```

  
##What does the drv variable describe? Read the help for ?mpg to find out.
```{r}
?mpg
#f = front-wheel drive, r = rear wheel drive, 4 = 4wd
```

  
##Make a scatterplot of hwy vs cyl.
```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = hwy, y = cyl))
```
  
##What happens if you make a scatterplot of class vs drv. Why is the plot not useful?
```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = class, y = drv))#it's not visualized, no meaningful
```

  
#practise for Aesthetic mapping
  
##by color
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = class))
```
  
##by size
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, size = class))
```
  
##by alpha aesthetic
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, alpha = class))
```
  
##by shape aesthetic
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, shape = class))
```
  
##change the color for the basic aesthetic
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy), color = "blue")
```

  
#practise in 3.3.1
  
##What’s gone wrong with this code? Why are the points not blue?
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = "blue"))
#the color need to go outside of aes(), if I want to change the color of the point
```
  
##Which variables in mpg are categorical? Which variables are continuous? (Hint: type ?mpg to read the documentation for the dataset). How can you see this information when you run mpg?
```{r}
?mpg
mpg
##"manufacturer","model","trans","drv", "fl", and "class" are categorials
##"displ","year","cyl", "cty", and "hwy" are continuous

##let test by plot
hist(mpg$displ)
hist(mpg$year)
hist(mpg$cyl)
hist(mpg$cty)#normal distribution
hist(mpg$hwy)#normal distribution

```
  
##Map a continuous variable to color, size, and shape. How do these aesthetics behave differently for categorical vs. continuous variables?
  
###color
```{r}
mpg
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = cty))

#the colors are also continuous, so it is hard to tell the difference between different continuous variables
```
  
###size
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, size = cty))
```
  
###shape
```{r}
#mpg
#ggplot(data = mpg) + 
  #geom_point(mapping = aes(x = displ, y = hwy, shape = class))
#A continuous variable can not be mapped to shape
```
  
##What happens if you map the same variable to multiple aesthetics?
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = displ, color = displ))

#it will become a great correlation line 
```
  
##What does the stroke aesthetic do? What shapes does it work with? (Hint: use ?geom_point)
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy,color = model), stroke = 1)

?geom_point
#it can be used to change the size of the points in the plot
```
  
##What happens if you map an aesthetic to something other than a variable name, like aes(colour = displ < 5)?
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy,color = displ < 5), stroke = 1)
```

  
#practise on 'Facets' part. One way to add additional variables is with aesthetics, particularly useful for categorical variables.
  
##facet_wrap, to facet your plot by a single variable. The variable that you pass to facet_wrap() should be discrete.
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ class, nrow = 2)
```

  
##facet_grid, to facet your plot on the combination of two variables, or one variable
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_grid(drv ~ cyl)
```
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_grid(.~ cyl)
```
  
#3.5.1 Excercises
  
##1.What happens if you facet on a continuous variable?
  
###facet_wrap
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ cty, nrow = 2)
```
  
###try to facet_grid the continuous variable
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_grid(~ cty)
```
  
##2.What do the empty cells in plot with facet_grid(drv ~ cyl) mean? How do they relate to this plot?
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = drv, y = cyl))

#there are no points when drv equals to "4" and cyl equals to "5"
```
  
##3.What plots does the following code make? What does . do?
  
###facet only in y-axies
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(drv ~ .)

?facet_grid
```
  
###facet only in x-axies
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(. ~ cyl)
```
  
##4.Take the first faceted plot in this section:
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color=class)) + 
  facet_wrap(~ class, nrow = 2)

#it gives us more information for a specified model
```
  
###What are the advantages to using faceting instead of the colour aesthetic? 
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = class))
```

  
###What are the disadvantages?
  
####There is less data in each figure, we can't see a strong negative relationship between displ and hwy as it was displayed in the color aesthetic figure.

  
###How might the balance change if you had a larger dataset?
  
####Each figure may have a strong negative relationships between displ and hwy.

  
##5.Read ?facet_wrap. What does nrow do? What does ncol do?
```{r}
?facet_wrap

#nrow and ncol represented the number of rows and columns will be created when you facet_warp your original plot.
```

  
###What other options control the layout of the individual panels? 
  
#####Try scales, which can allow scales to vary across the panels
```{r}
ggplot(mpg, aes(displ, hwy)) +
  geom_point() +
  facet_wrap(~c("cyl", "drv"), scales = "free")

```
  
####Try labeller, which control how labels are printed in panels
```{r}
ggplot(mpg, aes(displ, hwy)) +
  geom_point() +
  facet_wrap(c("cyl", "drv"), labeller = "label_both")
```
  
####Try as.table, if can change the position of the panel according to the values. If TRUE, the default, the facets are laid out like a table with highest values at the bottom-right. If FALSE, the facets are laid out like a plot with the highest value at the top-right.
```{r}
ggplot(mpg, aes(displ, hwy)) +
  geom_point() +
  facet_wrap(c("cyl", "drv"), as.table = FALSE)
```
  
####Try switch. Change the position of the labels. If "x", the top labels will be displayed to the bottom. If "y", the right-hand side labels will be displayed to the left. Can also be set to "both".
```{r}
ggplot(mpg, aes(displ, hwy)) +
  geom_point() +
  facet_wrap(c("cyl", "drv"), switch = "y")
```
  
####Try drop ?
```{r}
ggplot(mpg, aes(displ, hwy)) +
  geom_point() +
  facet_wrap(c("cyl", "drv"), drop = FALSE)
```
  
####Try strip.position, can place the labels on either of the four sides
```{r}
ggplot(mpg, aes(displ, hwy)) +
  geom_point() +
  facet_wrap(c("cyl", "drv"), strip.position ="right")
```
  
####Try shrink
```{r}
par(mfrow=c(1,2))
ggplot(mpg, aes(displ, hwy)) +
  geom_point() +
  facet_wrap(c("cyl", "drv"), shrink =TRUE)

ggplot(mpg, aes(displ, hwy)) +
  geom_point() +
  facet_wrap(c("cyl", "drv"), shrink =FALSE)
##There's no difference???
```

  
###Why doesn’t facet_grid() have nrow and ncol variables?
```{r}
?facet_grid

##it was faceted according to the levels of variables. The number of rows or columns were determined by the levels of the variable.
```

